---
title: "knot_descriptives"
author: "sven panis"
date: "2024-06-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-packages, include=F}
library(tidyverse) # data wrangling
library(patchwork) # combine figures
```

# Calculate mean RTs to compare with reported values

```{r}
# load the datafile
#data_orig <- read_csv(file = "data/data.csv") # 15120 obs. of 17 variables
# 14668 trials with data

data_orig2 <-read_csv(file = "data/data_mat4.csv") # 14746 obs. of 10 variables
summary(data_orig2)

# check
test <- data_orig2 %>% group_by(pid, day, session) %>% summarise(N = n())
print.data.frame(test)

# Missing 11 sessions (of 200 sessions): 
# s2 of d1 of s1
# s2 of d2 of s3
# s2 of d5 of s3
# s1 of d2 of s7
# s2 of d1 of s14
# s2 of d1 of s15
# s2 of d2 of s15
# s2 of d1 of s16
# s2 of d2 of s17
# s2 of d3 of s17
# s2 of d5 of s17 -> present in data_4mat.csv !! 78 extra trials

# remove trials where response = NA (452 trials)
data2 <- data_orig %>% drop_na() # 14668 trials left
head(data2)

# select relevant variables, and add accuracy column
data2 <- data2 %>%
  select(pid, RESPONSE, RT, GROUP, MATCH, DAY, SESSION) %>%
  mutate(acc = ifelse(RESPONSE==MATCH,1,0))
head(data2)

# select correct trials
data2_acc <- data2 %>% filter(acc==1) # 12783 trials
head(data2_acc)

# eliminate fastest and slowest 10% of trials, for each testing session of 80 trials:

# combine day and session info
data2_acc <- data2_acc %>% mutate(testsession = (2*(DAY-1)) + SESSION )

# nest data within pid x testsession
data2_acc_nest <- data2_acc %>% group_nest(pid,testsession)

pluck(data2_acc_nest,3,1)

# define function to sort RT, calculate 10%, and remove slowest and fastest trials
trim_data <- function(df){
  df <- df %>% arrange(RT)
  Ntrials <- nrow(df) 
  Nperc <- floor(floor(Ntrials/10) / 2) 
  df <- df %>% mutate(trim=1) # column 8
  df[1:Nperc,8] <- 0
  df[(nrow(df)-Nperc):nrow(df),8] <- 0
  df <- df %>% filter(trim==1)
  return(df)
}

data2_acc_trim <- data2_acc_nest %>% 
                     mutate(trimmed  = map(data, trim_data)) 

pluck(data2_acc_trim,4,1)

# unnest
data3 <- data2_acc_trim %>% 
                        select(pid, testsession, trimmed) %>%  unnest(trimmed)
head(data3)
summary(data3)

# plot mean RT for session 2
data3 <- data3 %>% mutate(GROUP = factor(GROUP, levels = 1:4))
data3 %>% filter(SESSION==2) %>% 
  group_by(DAY, GROUP) %>% summarise(meanRT = mean(RT)) %>%
  ggplot(mapping = aes(DAY, meanRT, group=GROUP, color=GROUP)) + geom_line()
```

# Calculate EHA descriptive statistics for the behavioral data of Cross et. al (2012).

## Separately for each subject.

```{r}
# load the datafile
# data_orig <- read_csv(file = "data/data.csv") # 15120 obs. of 17 variables
data_orig2 <- read_csv(file = "data/data_mat4.csv") # 14746 obs. of 10 variables (NA removed, renamed variables, accuracy added)
summary(data_orig2)
data_orig2 %>% head(n=20)

# pid: 1-20 ? 
# rt: 375-2499 ms / NA: 452
# response: 1 = match, 2 = nomatch / NA: 452
# condition: 1 - 4
# match: 1 = yes, 2 = no
# day: 1 - 5

# Rename columns to match with functions: iv1=day, iv2=condition
names(data_orig2) <- c("pid", "iv1", "session", "trial_session", "iv2", "cond_name", "match", "response", "RT", "acc")
head(data_orig2)

# Add trial number per subject (total)
data <- data_orig2 %>% group_by(pid) %>% mutate(trial = row_number()) %>% ungroup()
head(data)
summary(data)

# remove trials where response = NA
#data <- data %>% drop_na() # 14668 trials left

# add condition indicating each combination of iv2 (condition) and iv1 (day)
data <- data %>% mutate(condition = (4*(iv1-1)) + iv2) 
head(data) 
summary(data)

# make cond_name a factor
data <- data %>% 
  mutate(cond_name = factor(cond_name, levels=c("name", "tie", "both", "none")))
summary(data)

# visualize distribution per subject
data %>% ggplot(aes(x=RT)) +
  geom_histogram(binwidth=20) +
  facet_wrap(~pid)
```

Nest data within participants.

```{r nest-subjects}
data_nested <- data %>% group_nest(pid)
```

Now define and apply various functions using map and map2, to set-up life tables and create plots showing the descriptive functions of discrete time.

```{r func-define-censoring-drt}
censor <- function(df, timeout, bin_width){
  if(!(timeout %% bin_width == 0)){
    return("The censoring time must be a multiple of the bin width!")
  }
  df %>% mutate(right_censored = 0,
                RT2 = ifelse(RT > timeout, timeout, RT) %>% round(digits=2),
                right_censored = ifelse(RT2 == timeout,1,right_censored),
                dRT = ceiling(RT2/bin_width),
                cens_time = timeout, bin_width = bin_width)
}
```

```{r func-setup-ptb}
ptb <- function(df){
  df %>% uncount(weights = dRT) %>% 
         group_by(trial) %>% 
         mutate(period = 1:n()) %>% 
         mutate(event = if_else(period == max(period) & right_censored == 0, 1, 0)) %>% 
         ungroup()
}
```

```{r func-setup-lifetable}
setup_lt_2iv <- function(ptb){
  ptb %>% mutate(event = str_c("event", event)) %>%
          group_by(condition, iv1, iv2, period) %>% 
          count(event) %>% 
          ungroup() %>% 
          pivot_wider(names_from = event,
                      values_from = n) %>% 
          mutate(event0 = ifelse(is.na(event0),0,event0), # replace NA with 0
                 event1 = ifelse(is.na(event1),0,event1),
                 risk_set = event0 + event1) %>% # define the risk set
          mutate(hazard = (event1 / risk_set) %>% round(digits = 3)) %>% # calculate hazard estimate
          mutate(se_haz = sqrt((hazard * (1 - hazard)) / risk_set) %>% round(digits = 4)) %>% # se hazard
          group_by(condition) %>%
          mutate(survival = (cumprod(1-hazard)) %>% round(digits = 4), # calculate survival estimate
                 term     = (cumsum(hazard / (risk_set * (1 - hazard)))) %>% round(digits = 7),
                 se_surv  = (survival * sqrt(term)) %>% round(digits = 5)  ) %>% # Greenwood's (1926) approximation
          ungroup() 
}
```

```{r func-conditional-accuracy}
calc_ca <- function(df){
  df %>% filter(right_censored==0) %>%
         group_by(condition,dRT,cens_time,bin_width) %>%
         summarize(ca = mean(acc) %>% round(digits = 2),
                   n = n(),
                   .groups = 'drop') %>%
         ungroup() %>%
         mutate(period = dRT,
                se_ca = sqrt((ca * (1-ca)) / n) %>% round(digits = 3)) %>%
         select(-dRT)
}
```

```{r func-join}
join_lt_ca <- function(df1,df2){df1 %>% left_join(df2, join_by(condition,period))}
```

```{r func-extract-median}
extract_median <- function(df){
  above_pct50 <- df %>% 
      group_by(condition) %>%
      filter(survival > .5) %>% 
      slice(n()) # take last row
  below_pct50 <- df %>% 
      group_by(condition) %>%
      filter(survival < .5) %>% 
      slice(1) # take first row
  # pull period above
  period_above <- pull(above_pct50, period)
  # pull survivor function values
  survival_above <- pull(above_pct50, survival)
  survival_below <- pull(below_pct50, survival)
  # estimate median by interpolation
  median_period <- period_above+((survival_above-.5)/(survival_above-survival_below))*((period_above+1)-period_above)
}
```

```{r func-make-plot-2iv}
plot_eha_2iv <- function(df,subj){
  library(patchwork)
  cutoff <- df %>% pull(cens_time) %>% max(na.rm=T)
  binsize <- df %>% pull(bin_width) %>% max(na.rm=T)
  median_period <- extract_median(df)
  n_iv1 <- nlevels(factor(df$iv1))
  n_iv2 <- nlevels(factor(df$iv2))
  n_conditions <- n_iv1*n_iv2
  # set up tibble to plot vertical lines indicating S(t).50 for each condition
  data_median <- c()
  for(i in 1:n_conditions){
    data_median <- append(data_median, c(median_period[i], median_period[i]))
  }
  data_medians <- tibble(period= data_median,
                         survival = rep(c(.5, 0),n_conditions),
                         condition = rep(1:n_conditions, each=2),
                         train =  factor(rep(rep(1:n_iv2, each=2),n_iv1),levels=c(1:4),labels=c("naming", "tying", "naming+tying","no training")),
                         day = factor(rep(1:n_iv1, each=2*n_iv2),levels=c(1:5),labels=str_c("day ",1:5)  ))
  
p1 <-df %>% 
  mutate(day = factor(iv1,levels=c(1:5),labels=str_c("day ",1:5)  )) %>% 
  mutate(train = factor(iv2,levels=c(1:4),labels=c("naming", "tying", "naming+tying","no training")  )) %>% 
                           
  ggplot(aes(x=period, color=train, group=train)) +
  geom_line(aes(y=hazard)) +
  geom_point(aes(y=hazard), size=1) + labs(color="Training condition") +
  geom_linerange(aes(ymin=hazard-se_haz, ymax=hazard+se_haz), show.legend = F) +
  scale_x_continuous(breaks = c(0,1:(cutoff/binsize)), labels=c(0,1:(cutoff/binsize)*binsize),
                     limits = c(0,cutoff/binsize)) +
  scale_y_continuous(limits = c(0,1)) +
  labs(x="", y="h(t)", title = paste("Subject ", subj)) +
  theme(legend.background = element_rect(fill = "transparent"),
        panel.grid = element_blank(),
        legend.position = "top",
        axis.text.x = element_text(angle=90)) +
  facet_wrap(~day, nrow=1,ncol=5)

p2 <-df %>%
  mutate(day = factor(iv1,levels=c(1:5),labels=str_c("day ",1:5)  )) %>% 
  mutate(train = factor(iv2,levels=c(1:4),labels=c("naming", "tying", "naming+tying", "no training")  )) %>% 
  ggplot(aes(x=period, color=train, group=train)) +
  geom_line(aes(y=survival), show.legend = F) +
  geom_point(aes(y=survival), size=1, show.legend = F) +
  
  geom_linerange(aes(ymin=survival-se_surv, ymax=survival+se_surv), show.legend = F) +
  # add medians
  geom_path(aes(x=period, y=survival),
            data = data_medians, 
            linetype = 1, show.legend = F) +
  scale_x_continuous(breaks = c(0,1:(cutoff/binsize)), labels=c(0,1:(cutoff/binsize)*binsize),
                     limits=c(0,cutoff/binsize)) +
  scale_y_continuous(limits = c(0,1)) +
  labs(x="", y="S(t)") +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle=90)) +
  facet_wrap(~day, nrow=1,ncol=5)

p3 <-df %>%
  mutate(day = factor(iv1,levels=c(1:5),labels=str_c("day ",1:5)  )) %>% 
  mutate(train = factor(iv2,levels=c(1:4),labels=c("naming", "tying", "naming+tying","no training")  )) %>% 
  ggplot(aes(x=period, color=train, group=train)) +
  geom_line(aes(y=ca), show.legend = F) +
  geom_point(aes(y=ca), size=1, show.legend = F) +
  geom_linerange(aes(ymin=ca-se_ca, ymax=ca+se_ca), show.legend = F) +
  scale_x_continuous(breaks = c(0,1:(cutoff/binsize)), labels=c(0,1:(cutoff/binsize)*binsize),
                     limits=c(0,cutoff/binsize)) +
  scale_y_continuous(limits = c(0,1)) +
  labs(x="Time bin t's endpoint (ms)", y="ca(t)",
       colour="Condition") +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle=90)) +
  facet_wrap(~day, nrow=1,ncol=5)

p1/p2/p3
}
```

Apply the functions using map and map2 to create the life tables and plots, for each participant.

```{r apply-functions}
data_final <- data_nested %>% 
                     mutate(censored  = map(data, censor, 1500, 75)) %>%  # user input: censoring time, bin width
                     mutate(ptb_data  = map(censored, ptb)) %>%            # create person-trial-bin dataset
                     mutate(lifetable = map(ptb_data, setup_lt_2iv)) %>%   # create life tables without ca for 2 IV's
                     mutate(condacc   = map(censored, calc_ca)) %>%        # calculate ca
                     mutate(lifetable_ca = map2(lifetable, condacc, join_lt_ca)) %>%  # create life tables with ca
                     mutate(plot      = map2(.x = lifetable_ca, .y = pid, plot_eha_2iv))  # create plots of info in life tables for 2 IV's
```

```{r extract-info}
# pull censored for subject 1
pluck(data_final,3,1)

# pull ptb for subject 2
pluck(data_final,4,2)

# pull lifetable for subject 20 and condition 1 (day1 and training condition 1)
pluck(data_final,5,20) %>% filter(condition==4)

# pull full lifetable for subject 1 and condition 20
pluck(data_final,7,1) %>% filter(condition==20)

# view plot for single subject 
pluck(data_final,8,3) # subjects 3,4, 7,10, 16, 18 and 19 responded slower in one or more training conditions, on 1 or more days compared to others (median RT > 1500)
```

## Aggregated across subjects

Make 1 plot for all data.
This requires a single pid, and a trial column that identifies each unique trial.

```{r}
# create new pid and trial variables
data_single <- data %>% mutate(oldtrial=trial,
                               oldpid=pid,
                               trial = 1:n(),
                               pid = 1)
summary(data_single)
head(data_single)
```


```{r func-make-plot-2iv}
# limit y-axis for hazard plot
plot_eha_2iv_lim <- function(df,subj){
  library(patchwork)
  cutoff <- df %>% pull(cens_time) %>% max(na.rm=T)
  binsize <- df %>% pull(bin_width) %>% max(na.rm=T)
  median_period <- extract_median(df)
  n_iv1 <- nlevels(factor(df$iv1))
  n_iv2 <- nlevels(factor(df$iv2))
  n_conditions <- n_iv1*n_iv2
  # set up tibble to plot vertical lines indicating S(t).50 for each condition
  data_median <- c()
  for(i in 1:n_conditions){
    data_median <- append(data_median, c(median_period[i], median_period[i]))
  }
  data_medians <- tibble(period= data_median,
                         survival = rep(c(.5, 0),n_conditions),
                         condition = rep(1:n_conditions, each=2),
                         train =  factor(rep(rep(1:n_iv2, each=2),n_iv1),levels=c(1:4),labels=c("naming", "tying", "naming+tying","no training")),
                         day = factor(rep(1:n_iv1, each=2*n_iv2),levels=c(1:5),labels=str_c("day ",1:5)  ))
  
p1 <-df %>% 
  mutate(day = factor(iv1,levels=c(1:5),labels=str_c("day ",1:5)  )) %>% 
  mutate(train = factor(iv2,levels=c(1:4),labels=c("naming", "tying", "naming+tying","no training")  )) %>% 
                           
  ggplot(aes(x=period, color=train, group=train)) +
  geom_line(aes(y=hazard)) +
  geom_point(aes(y=hazard), size=1) + labs(color="Training condition") +
  geom_linerange(aes(ymin=hazard-se_haz, ymax=hazard+se_haz), show.legend = F) +
  scale_x_continuous(breaks = c(0,1:(cutoff/binsize)), labels=c(0,1:(cutoff/binsize)*binsize),
                     limits = c(0,cutoff/binsize)) +
  scale_y_continuous(limits = c(0,.3)) + # changes
  labs(x="", y="h(t)", title = paste("Subject ", subj)) +
  theme(legend.background = element_rect(fill = "transparent"),
        panel.grid = element_blank(),
        legend.position = "top",
        axis.text.x = element_text(angle=90)) +
  facet_wrap(~day, nrow=1,ncol=5)

p2 <-df %>%
  mutate(day = factor(iv1,levels=c(1:5),labels=str_c("day ",1:5)  )) %>% 
  mutate(train = factor(iv2,levels=c(1:4),labels=c("naming", "tying", "naming+tying", "no training")  )) %>% 
  ggplot(aes(x=period, color=train, group=train)) +
  geom_line(aes(y=survival), show.legend = F) +
  geom_point(aes(y=survival), size=1, show.legend = F) +
  
  geom_linerange(aes(ymin=survival-se_surv, ymax=survival+se_surv), show.legend = F) +
  # add medians
  geom_path(aes(x=period, y=survival),
            data = data_medians, 
            linetype = 1, show.legend = F) +
  scale_x_continuous(breaks = c(0,1:(cutoff/binsize)), labels=c(0,1:(cutoff/binsize)*binsize),
                     limits=c(0,cutoff/binsize)) +
  scale_y_continuous(limits = c(0,1)) +
  labs(x="", y="S(t)") +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle=90)) +
  facet_wrap(~day, nrow=1,ncol=5)

p3 <-df %>%
  mutate(day = factor(iv1,levels=c(1:5),labels=str_c("day ",1:5)  )) %>% 
  mutate(train = factor(iv2,levels=c(1:4),labels=c("naming", "tying", "naming+tying","no training")  )) %>% 
  ggplot(aes(x=period, color=train, group=train)) +
  geom_line(aes(y=ca), show.legend = F) +
  geom_point(aes(y=ca), size=1, show.legend = F) +
  geom_linerange(aes(ymin=ca-se_ca, ymax=ca+se_ca), show.legend = F) +
  scale_x_continuous(breaks = c(0,1:(cutoff/binsize)), labels=c(0,1:(cutoff/binsize)*binsize),
                     limits=c(0,cutoff/binsize)) +
  scale_y_continuous(limits = c(0,1)) +
  labs(x="Time bin t's endpoint (ms)", y="ca(t)",
       colour="Condition") +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle=90)) +
  facet_wrap(~day, nrow=1,ncol=5)

p1/p2/p3
}
```

```{r}
data_nested_single <- data_single %>% group_nest(pid)

data_final_single <- data_nested_single %>% 
                     mutate(censored  = map(data, censor, 1500, 75)) %>%  # user input: censoring time, bin width
                     mutate(ptb_data  = map(censored, ptb)) %>%            # create person-trial-bin dataset
                     mutate(lifetable = map(ptb_data, setup_lt_2iv)) %>%   # create life tables without ca for 2 IV's
                     mutate(condacc   = map(censored, calc_ca)) %>%        # calculate ca
                     mutate(lifetable_ca = map2(lifetable, condacc, join_lt_ca)) %>%  # create life tables with ca
                     mutate(plot      = map2(.x = lifetable_ca, .y = pid, plot_eha_2iv_lim))  # create plots of info in life tables for 2 IV's
```


```{r}
# view plot for subject 1
pluck(data_final_single,8,1)
```


```{r}
# save as pdf
# map2(paste0("figures/figure_aggregated", data_final_single$pid, ".pdf"), data_final_single$plot, ggsave, width = 25, height = 20, units = "cm")

# save as png
map2(paste0("figures/figure_aggregated", data_final_single$pid, ".png"), data_final_single$plot, ggsave, width = 12, height = 8, dpi = 600)

```

## Calculate descriptive EHA stats for Pre- and Post-training sessions separately (aggregated data)

Pre-training sessions aggregated data

```{r}
# select pre-training sessions
data_pre <- data %>% filter(session == 1)
head(data_pre)
# create new pid and trial variables for aggregated data plot
data_pre_single <- data_pre %>% mutate(oldtrial=trial,
                                              oldpid=pid,
                                              trial = 1:n(),
                                              pid = 1)
summary(data_pre_single)
head(data_pre_single)
```

```{r}
data_nested_single_pre <- data_pre_single %>% group_nest(pid)

data_final_single_pre <- data_nested_single_pre %>% 
                     mutate(censored  = map(data, censor, 1500, 75)) %>%  # user input: censoring time, bin width
                     mutate(ptb_data  = map(censored, ptb)) %>%            # create person-trial-bin dataset
                     mutate(lifetable = map(ptb_data, setup_lt_2iv)) %>%   # create life tables without ca for 2 IV's
                     mutate(condacc   = map(censored, calc_ca)) %>%        # calculate ca
                     mutate(lifetable_ca = map2(lifetable, condacc, join_lt_ca)) %>%  # create life tables with ca
                     mutate(plot      = map2(.x = lifetable_ca, .y = pid, plot_eha_2iv_lim))  # create plots of info in life tables for 2 IV's
```

```{r}
# view plot for aggregated data
pluck(data_final_single_pre,8,1)
```


```{r}
# save as png
map2(paste0("figures/figure_aggregated_pre", data_final_single_pre$pid, ".png"), data_final_single_pre$plot, ggsave, width = 12, height = 8, dpi = 600)
```


Post-training sessions aggregated data

```{r}
# select post-training sessions
data_post <- data %>% filter(session == 2)

# create new pid and trial variables for aggregated data plot
data_post_single <- data_post %>% mutate(oldtrial=trial,
                                              oldpid=pid,
                                              trial = 1:n(),
                                              pid = 1)
summary(data_post_single)
head(data_post_single)
```

```{r}
data_nested_single_post <- data_post_single %>% group_nest(pid)

data_final_single_post <- data_nested_single_post %>% 
                     mutate(censored  = map(data, censor, 1500, 75)) %>%  # user input: censoring time, bin width
                     mutate(ptb_data  = map(censored, ptb)) %>%            # create person-trial-bin dataset
                     mutate(lifetable = map(ptb_data, setup_lt_2iv)) %>%   # create life tables without ca for 2 IV's
                     mutate(condacc   = map(censored, calc_ca)) %>%        # calculate ca
                     mutate(lifetable_ca = map2(lifetable, condacc, join_lt_ca)) %>%  # create life tables with ca
                     mutate(plot      = map2(.x = lifetable_ca, .y = pid, plot_eha_2iv_lim))  # create plots of info in life tables for 2 IV's
```

```{r}
# view plot for aggregated data
pluck(data_final_single_post,8,1)
```


```{r}
# save as png
map2(paste0("figures/figure_aggregated_post", data_final_single_post$pid, ".png"), data_final_single_post$plot, ggsave, width = 12, height = 8, dpi = 600)
```

## Calculate descriptive EHA stats for the four between-training periods

4 between-training sessions aggregated data (first and last session removed)

```{r}
# select between-training sessions
head(data)
summary(data)
data_between <- data %>%
  mutate(day_between = ifelse(iv1==1 & session ==1, 0,
                       ifelse(iv1==1 & session ==2, 1,
                       ifelse(iv1==2 & session ==1, 1,
                       ifelse(iv1==2 & session ==2, 2,
                       ifelse(iv1==3 & session ==1, 2,
                       ifelse(iv1==3 & session ==2, 3,
                       ifelse(iv1==4 & session ==1, 3,
                       ifelse(iv1==4 & session ==2, 4,
                       ifelse(iv1==5 & session ==1, 4, 0))))))))) )
data_between %>% count(day_between)
head(data_between)

# remove first and last session
data_between <- data_between %>% filter(day_between>0)
summary(data_between)

# remove iv1 and session
data_between <- data_between %>% select(-c(iv1,session))
summary(data_between)

# create new condition levels
data_between <- data_between %>% mutate(condition = (4*(day_between-1)) + iv2) 
summary(data_between)

# Rename columns to match with functions
names(data_between) <- c("pid", "trial_session","iv2", "cond_name","match", "response","RT","acc", "trial","condition","iv1")
head(data_between)

# create new pid and trial variables for aggregated data plot
data_between_single <- data_between %>% mutate(oldtrial=trial,
                                              oldpid=pid,
                                              trial = 1:n(),
                                              pid = 1)
summary(data_between_single)
head(data_between_single)
```

```{r func-make-plot-2iv}
# limit y-axis hazard + only 4 levels for iv1 (periods between learning)
plot_eha_2iv_lim_between <- function(df,subj){
  library(patchwork)
  cutoff <- df %>% pull(cens_time) %>% max(na.rm=T)
  binsize <- df %>% pull(bin_width) %>% max(na.rm=T)
  median_period <- extract_median(df)
  n_iv1 <- nlevels(factor(df$iv1))
  n_iv2 <- nlevels(factor(df$iv2))
  n_conditions <- n_iv1*n_iv2
  # set up tibble to plot vertical lines indicating S(t).50 for each condition
  data_median <- c()
  for(i in 1:n_conditions){
    data_median <- append(data_median, c(median_period[i], median_period[i]))
  }
  data_medians <- tibble(period= data_median,
                         survival = rep(c(.5, 0),n_conditions),
                         condition = rep(1:n_conditions, each=2),
                         train =  factor(rep(rep(1:n_iv2, each=2),n_iv1),levels=c(1:4),labels=c("naming", "tying", "naming+tying","no training")),
                         day = factor(rep(1:n_iv1, each=2*n_iv2),levels=c(1:4),labels=str_c("period ",1:4)  )) # changes
  
p1 <-df %>% 
  mutate(day = factor(iv1,levels=c(1:4),labels=str_c("period ",1:4)  )) %>% # changes 
  mutate(train = factor(iv2,levels=c(1:4),labels=c("naming", "tying", "naming+tying","no training")  )) %>% 
                           
  ggplot(aes(x=period, color=train, group=train)) +
  geom_line(aes(y=hazard)) +
  geom_point(aes(y=hazard), size=1) + labs(color="Training condition") +
  geom_linerange(aes(ymin=hazard-se_haz, ymax=hazard+se_haz), show.legend = F) +
  scale_x_continuous(breaks = c(0,1:(cutoff/binsize)), labels=c(0,1:(cutoff/binsize)*binsize),
                     limits = c(0,cutoff/binsize)) +
  scale_y_continuous(limits = c(0,.3)) +
  labs(x="", y="h(t)", title = paste("Subject ", subj)) +
  theme(legend.background = element_rect(fill = "transparent"),
        panel.grid = element_blank(),
        legend.position = "top",
        axis.text.x = element_text(angle=90)) +
  facet_wrap(~day, nrow=1,ncol=5)

p2 <-df %>%
  mutate(day = factor(iv1,levels=c(1:4),labels=str_c("period ",1:4)  )) %>% # changes
  mutate(train = factor(iv2,levels=c(1:4),labels=c("naming", "tying", "naming+tying", "no training")  )) %>% 
  ggplot(aes(x=period, color=train, group=train)) +
  geom_line(aes(y=survival), show.legend = F) +
  geom_point(aes(y=survival), size=1, show.legend = F) +
  
  geom_linerange(aes(ymin=survival-se_surv, ymax=survival+se_surv), show.legend = F) +
  # add medians
  geom_path(aes(x=period, y=survival),
            data = data_medians, 
            linetype = 1, show.legend = F) +
  scale_x_continuous(breaks = c(0,1:(cutoff/binsize)), labels=c(0,1:(cutoff/binsize)*binsize),
                     limits=c(0,cutoff/binsize)) +
  scale_y_continuous(limits = c(0,1)) +
  labs(x="", y="S(t)") +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle=90)) +
  facet_wrap(~day, nrow=1,ncol=5)

p3 <-df %>%
  mutate(day = factor(iv1,levels=c(1:4),labels=str_c("period ",1:4)  )) %>% # changes 
  mutate(train = factor(iv2,levels=c(1:4),labels=c("naming", "tying", "naming+tying","no training")  )) %>% 
  ggplot(aes(x=period, color=train, group=train)) +
  geom_line(aes(y=ca), show.legend = F) +
  geom_point(aes(y=ca), size=1, show.legend = F) +
  geom_linerange(aes(ymin=ca-se_ca, ymax=ca+se_ca), show.legend = F) +
  scale_x_continuous(breaks = c(0,1:(cutoff/binsize)), labels=c(0,1:(cutoff/binsize)*binsize),
                     limits=c(0,cutoff/binsize)) +
  scale_y_continuous(limits = c(0,1)) +
  labs(x="Time bin t's endpoint (ms)", y="ca(t)",
       colour="Condition") +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(angle=90)) +
  facet_wrap(~day, nrow=1,ncol=5)

p1/p2/p3
}
```



```{r}
data_nested_single_between <- data_between_single %>% group_nest(pid)

data_final_single_between <- data_nested_single_between %>% 
                     mutate(censored  = map(data, censor, 1500, 75)) %>%  # user input: censoring time, bin width
                     mutate(ptb_data  = map(censored, ptb)) %>%            # create person-trial-bin dataset
                     mutate(lifetable = map(ptb_data, setup_lt_2iv)) %>%   # create life tables without ca for 2 IV's
                     mutate(condacc   = map(censored, calc_ca)) %>%        # calculate ca
                     mutate(lifetable_ca = map2(lifetable, condacc, join_lt_ca)) %>%  # create life tables with ca
                     mutate(plot      = map2(.x = lifetable_ca, .y = pid, plot_eha_2iv_lim_between))  # create plots of info in life tables for 2 IV's
```

```{r}
# view plot for subject 1
pluck(data_final_single_between,8,1)
```


```{r}
# save as png
map2(paste0("figures/figure_aggregated_between", data_final_single_between$pid, ".png"), data_final_single_between$plot, ggsave, width = 12, height = 8, dpi = 600)
```


# check which subjects have at least 80% of their data in the range 600 - 1500 (12 bins of 75 ms)

```{r}
summary(data)
head(data)

data_test <- data %>% mutate(range = ifelse(RT < 600 | RT > 1500, 0,1))
head(data_test)
summary(data_test)

data_test %>% group_by(pid) %>% summarise(range_perc = mean(range))

# subjects 2, 3, 7,10, 16,17 and 19 have less than 80 percent of their RT in this range

# visualize distribution per subject
data %>% ggplot(aes(x=RT)) +
  geom_histogram(binwidth=20) +
  geom_vline(xintercept=600) +
  geom_vline(xintercept=1500) +
  facet_wrap(~pid)
```



## Apply clustering algorithm to identify groups of subjects?




